---
title: "Reproducible Research: Peer Assessment 1"
<<<<<<< HEAD
author: "PS"
date: "Monday, July 20, 2015"
output: html_document
---

###Loading and preprocessing the data

```{r,echo=TRUE}
activity <- read.csv("C:/Users/Prasanta/Documents/activity.csv")
head(activity)
```

```{r, echo=TRUE}
activity$date <- as.Date(activity$date, "%Y-%m-%d")
```

###What is mean total number of steps taken per day?


####1. Calculating the total number of steps taken per day

```{r, echo=TRUE}
StepsTotal <- aggregate(steps ~ date, data = activity, sum, na.rm = TRUE)
```

####2. Histogram of the total number of steps taken each day
```{r, echo=TRUE}
hist(StepsTotal$steps, main = "Total steps by day", xlab = "day", col = "blue")
```

####3. Mean and median of the total number of steps taken per day
```{r, echo=TRUE}
mean(StepsTotal$steps)
```
```{r, echo=TRUE}
median(StepsTotal$steps)
```


###What is the average daily activity pattern?

####1. Make a time series plot (i.e. type = "l") of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all days (y-axis)
```{r, echo=TRUE}
time_series <- tapply(activity$steps, activity$interval, mean, na.rm = TRUE)
plot(row.names(time_series), time_series, type = "l", xlab = "5-min interval", 
    ylab = "Average across all Days", main = "Average number of steps taken", 
    col = "blue")
```

####2. Which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps?
```{r, echo=TRUE}
max_interval <- which.max(time_series)
names(max_interval)
```

###Imputing missing values

####1. Calculate and report the total number of missing values in the dataset
```{r, echo=TRUE}
activity_NA <- sum(is.na(activity))
activity_NA
```

####2. Devise a strategy for filling in all of the missing values in the dataset
```{r, echo=TRUE}
StepsAverage <- aggregate(steps ~ interval, data = activity, FUN = mean)
fillNA <- numeric()
for (i in 1:nrow(activity)) {
    obs <- activity[i, ]
    if (is.na(obs$steps)) {
        steps <- subset(StepsAverage, interval == obs$interval)$steps
    } else {
        steps <- obs$steps
    }
    fillNA <- c(fillNA, steps)
}
```

####3. Create a new dataset that is equal to the original dataset but with the missing data filled in
```{r, echo=TRUE}
new_activity <- activity
new_activity$steps <- fillNA
```

####4. Make a histogram of the total number of steps taken each day and Calculate and report the mean and median total number of steps taken per day
```{r, echo=TRUE}
StepsTotal2 <- aggregate(steps ~ date, data = new_activity, sum, na.rm = TRUE)
hist(StepsTotal2$steps, main = "Total steps by day", xlab = "day", col = "red")
```

#######The mean and median is
```{r, echo=TRUE}
mean(StepsTotal2$steps)
```
```{r, echo=TRUE}
median(StepsTotal2$steps)
```


###Are there differences in activity patterns between weekdays and weekends?

####1. Create a new factor variable in the dataset with two levels - "weekday" and "weekend" indicating whether a given date is a weekday or weekend day
```{r, echo=TRUE}
day <- weekdays(activity$date)
daylevel <- vector()
for (i in 1:nrow(activity)) {
    if (day[i] == "Saturday") {
        daylevel[i] <- "Weekend"
    } else if (day[i] == "Sunday") {
        daylevel[i] <- "Weekend"
    } else {
        daylevel[i] <- "Weekday"
    }
}
activity$daylevel <- daylevel
activity$daylevel <- factor(activity$daylevel)

stepsByDay <- aggregate(steps ~ interval + daylevel, data = activity, mean)
names(stepsByDay) <- c("interval", "daylevel", "steps")
```

####2. Make a panel plot containing a time series plot (i.e. type = "l") of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all weekday days or weekend days (y-axis)
```{r, echo=TRUE}
library(lattice)
xyplot(steps ~ interval | daylevel, stepsByDay, type = "l", layout = c(1, 2), xlab = "Interval", ylab = "Number of steps")
```
=======
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data



## What is mean total number of steps taken per day?



## What is the average daily activity pattern?



## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
>>>>>>> 80edf39c3bb508fee88e3394542f967dd3fd3270
